Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-01-13 paper/paper.tex
define I
define m and n

\subsection*{Expert pre-screening}
Secondly, we reduce the number of IMTs in our study by focusing on those which are deemed to be most relevant.
Here, we define the relevance of an IMT as the possibility of imitating it by means of another IMT from a different instrument.
One example of such imitation is the acoustic similarity between slap tonguing in reed instruments and a snap pizzicato in strings instruments.
To collect perceptual ratings of relevance, we recruited two professors in music composition at the Paris Conservatory (CNSMDP), and explicitly gave them our definition of relevance.
Each of them inspected the entire corpus of $235$ IMTs and annotated them in terms of relevance according to a Likert scale with seven ticks.
In this Likert scale, the value 1 (least relevant) denotes that the IMT under consideration has a timbre that is idiosyncratic of the instrument, and that therefore, it is unlikely that humans will pair it with IMTs from other instruments.
Conversely, the value 7 (most relevant) denotes that the IMT under consideration has a strong similarity with IMTs from one or several other instruments.
Once both experts completed their annotation, we retained all IPTs whose average relevance score was judged equal to 3 or higher.
At the end of this stage of pre-screening, the list of IMT reduces from 235 to $N=78$.
Tables 1 and 2, in the Appendix section of this paper, give a full list of these 78 highly relevant IMTs.
It is worth noting that, according to both experts, the timbre of the accordion was judged too idiosyncratic, regardless of playing technique, to be relevant for this experiment.
Indeed, the accordion is the only instrument in the aforementioned list of 
instrument to have free reeds, keyboard-based actuation, or handheld airflow.

@@

\subsection*{Hypergraph partitioning}
Once the data collection campaign was complete, we analyzed the color assignments of each subject $k$ and converted them into a similarity graph $\mathcal{G}_k$, where the integer $k$ is an anonymized subject index, ranging between $1$ and $K$.
For a given $k$, the graph $\mathcal{G}_k$ contains $N=78$ vertices, each representing a different IMT in the corpus.
In $\mathcal{G}_k$, an edge connects any two vertices $i$ and $j$ if the corresponding dots in Cyberlioz have the same color.
Otherwise, there is no edge connecting $i$ and $j$.
This way, $\mathcal{G}_k$ contains as many connected components as the number of similarity clusters for the subject $k$, \ie{} the number of distinct colors on the Cyberlioz interface in the response of $k$.

>>>>

\subsection*{Expert pre-screening}
Secondly, we reduce the number of IMTs in our study by focusing on those which are deemed to be most relevant.
Here, we define the relevance of an IMT as the possibility of imitating it by means of another IMT from a different instrument.
One example of such imitation is the acoustic similarity between slap tonguing in reed instruments and a snap pizzicato in strings instruments.
To collect perceptual ratings of relevance, we recruited two professors in music composition at the Paris Conservatory (CNSMDP), and explicitly gave them our definition of relevance.
Each of them inspected the entire corpus of $235$ IMTs and annotated them in terms of relevance according to a Likert scale with seven ticks.
In this Likert scale, the value 1 (least relevant) denotes that the IMT under consideration has a timbre that is idiosyncratic of the instrument, and that therefore, it is unlikely that humans will pair it with IMTs from other instruments.
Conversely, the value 7 (most relevant) denotes that the IMT under consideration has a strong similarity with IMTs from one or several other instruments.
Once both experts completed their annotation, we retained all IPTs whose average relevance score was judged equal to 3 or higher.
At the end of this stage of pre-screening, the list of IMT reduces from 235 to $N=78$.
Tables 1 and 2, in the Appendix section of this paper, give a full list of these 78 highly relevant IMTs.
It is worth noting that, according to both experts, the timbre of the accordion was judged too idiosyncratic, regardless of playing technique, to be relevant for this experiment.
Indeed, the accordion is the only instrument in the aforementioned list of 
instrument to have free reeds, keyboard-based actuation, or handheld airflow.
Consequently, regardless of mute and technique, the number of instruments in our study is equal to $I=15$.

@@

\subsection*{Hypergraph partitioning}
Once the data collection campaign was complete, we analyzed the color assignments of each subject $k$ and converted them into a similarity graph $\mathcal{G}_k$, where the integer $k$ is an anonymized subject index, ranging between $1$ and $K$.
For a given $k$, the graph $\mathcal{G}_k$ contains $N=78$ vertices, each representing a different IMT in the corpus.
In $\mathcal{G}_k$, an edge connects any two vertices $m$ and $n$ if the corresponding dots in Cyberlioz have the same color.
Otherwise, there is no edge connecting $m$ and $n$.
This way, $\mathcal{G}_k$ contains as many connected components as the number of similarity clusters for the subject $k$, \ie{} the number of distinct colors on the Cyberlioz interface in the response of $k$.
